RDT - Gold Standard Equivalence

### 2022-01-25 RDT-equivalence.rmd
Update app and RMD to look at NegBin (num of tests required to detect)

>>>>

# Test Positive (Discounting Testing Rate)

Here, we're going to assume that the reference test is 100% sensitive and 100% specific. We're also going to discount the testing rate and the prevalence. The questions we're going to ask is:

1. If there are x disease positives, what is the distribution of test positives, given a certain sensitivity and specificity?
2. Given x disease positives, and the above distribution of test positives, how many additional test positives would be required such that y% of the distribution of positives was $\ge$ x?
  - **Is this just the negative binomial distribution?**

We'll start with the example of 3 disease positives, and a test of 80% sensitivity and 80% specificity.

```{r}
sens <- 0.8
spec <- 0.8

dis_pos <- 3
```

```{r}
test_pos <- tibble(positives = rbinom(1e5, dis_pos + 4, sens))
```

```{r}
ggplot(test_pos) +
  geom_bar(aes(x = positives))
```

```{r}
test_pos %>%
  summarize(
    mean = mean(positives),
    sd = sd(positives),
    min = min(positives),
    quantile_10 = quantile(positives, .10),
    quantile_25 = quantile(positives, .25),
    quantile_50 = quantile(positives, .50),
    quantile_75 = quantile(positives, .75),
    quantile_90 = quantile(positives, .90),
    max = max(positives)
  )
```

We can use the negative binomial to examine the number of tests required to achieve a certain level of disease positives. In the example below, we'll use the same sensitivity (80%) and disease positives (3).

```{r}
quant <- 0.95

total_test_dist <- tibble(
  failures = seq(0, qnbinom(p = quant, size = 3, prob = 0.4), 1),
  total = failures + dis_pos,
  dens = dnbinom(failures, 3, prob = 0.4),
  cum_prob = pnbinom(failures, 3, prob = 0.4)
  ) 
```

```{r}

qnbinom(p = quant, size = 3, prob = 0.8)
```

```{r}
total_test_dist %>%
  ggplot(aes(x = total, y = dens, fill = dens)) +
  geom_col()+
  scale_x_continuous(
    breaks = seq(min(total_test_dist$total), max(total_test_dist$total), 1)
    ) +
  geom_vline(xintercept = dis_pos + qnbinom(p = quant, size = 3, prob = 0.4)) +
  scale_fill_gradientn(colors = rev(met.brewer("Greek")))
```

```{r}
total_test_dist %>%
  ggplot() +
  geom_col(aes(x = total, y = cum_prob, fill = total)) +
  scale_x_continuous(
    breaks = seq(min(total_test_dist$total), max(total_test_dist$total), 1)
    ) +
  geom_hline(yintercept = quant) +
  geom_vline(xintercept = dis_pos + qnbinom(p = quant, size = 3, prob = 0.8)) +
  scale_fill_gradientn(colors = met.brewer("Hokusai2"))
```
